\section{Related Work}
FinDS-AgentBench sits at the intersection of agent benchmarks, machine-learning experimentation benchmarks, finance-domain LLM evaluation, and leakage-aware temporal validation. General agent and software-engineering benchmarks such as ~\cite{agentbench2023,swebench2023} emphasize multi-step execution, but do not target financial ML research validity.
ML-oriented agent benchmarks such as ~\cite{mlagentbench2023,mlebench2024,scienceagentbench2024,mlrbench2025} evaluate experimentation, engineering, or open-ended research automation. FinDS-AgentBench adopts their emphasis on executable artifacts while adding point-in-time finance data, temporal holdouts, leakage scanning, and writeup audit.
Finance benchmarks such as ~\cite{financebench2023,finben2024,profitmirage2025,fintoolbench2026,finmcpbench2026,workstreambench2026,bluefin2026} cover financial QA, broad financial LLM capabilities, leakage in financial agents, tool use, and spreadsheet workflows. These are adjacent but do not provide an end-to-end financial ML research benchmark with point-in-time task cards, private temporal labels, repeated-run uncertainty, reproducibility gates, and narrative-discipline scoring.
Data-science and data-analysis benchmarks such as ~\cite{ds10002022,infiagentdabench2024} motivate reliable code execution and analysis-task evaluation. FinDS-AgentBench extends that execution focus to financial research protocols where model validation, data timestamp availability, and claims about economic usefulness must be evaluated jointly.
Temporal-reasoning benchmarks such as ~\cite{temporalbench2026} motivate time-aware evaluation. FinDS-AgentBench narrows that lens to finance, where point-in-time information availability and leakage-safe validation are central rather than incidental constraints.

\begin{table}[t]
\centering
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{lll}
\toprule
Work & Neighbor Area & FinDS-AgentBench distinction \\
\midrule
AgentBench~\cite{agentbench2023} & General agent benchmark & Broad agent tasks; no financial ML protocol or point-in-time validity gates. \\
SWE-bench~\cite{swebench2023} & Software-engineering agent benchmark & Software repair rather than financial research notebooks and temporal holdouts. \\
DS-1000~\cite{ds10002022} & Data-science agent benchmark & Code-generation tasks rather than full financial ML research artifacts. \\
InfiAgent-DABench~\cite{infiagentdabench2024} & Data-science agent benchmark & General data analysis without finance-specific leakage and holdout discipline. \\
MLAgentBench~\cite{mlagentbench2023} & ML agent benchmark & ML experimentation without finance-specific data calendars or claim audit. \\
MLE-bench~\cite{mlebench2024} & ML agent benchmark & Kaggle-style ML engineering rather than financial temporal information discipline. \\
ScienceAgentBench~\cite{scienceagentbench2024} & General agent benchmark & Scientific workflows without market data, finance metrics, or investment-claim audit. \\
MLR-Bench~\cite{mlrbench2025} & ML agent benchmark & Open-ended ML research without finance leakage, private holdouts, or model-risk framing. \\
FinanceBench~\cite{financebench2023} & Finance-domain agent/LLM benchmark & Financial QA rather than executable financial ML research artifacts. \\
FinBen~\cite{finben2024} & Finance-domain agent/LLM benchmark & Broad financial LLM skills rather than validity-gated research workflows. \\
Profit Mirage / FinLake-Bench~\cite{profitmirage2025} & Finance-domain agent/LLM benchmark & Leakage-aware financial agents, but not reproducible research notebooks and audit cards. \\
TemporalBench~\cite{temporalbench2026} & Temporal reasoning benchmark & Time-series reasoning without financial ML artifacts and private temporal scoring. \\
FinToolBench~\cite{fintoolbench2026} & Finance-domain agent/LLM benchmark & Tool invocation rather than leakage-safe financial ML notebooks. \\
FinMCP-Bench~\cite{finmcpbench2026} & Finance-domain agent/LLM benchmark & MCP tool use rather than end-to-end financial ML research workflows. \\
WorkstreamBench~\cite{workstreambench2026} & Finance-domain agent/LLM benchmark & Spreadsheet workflows rather than temporal prediction and leakage-safe scoring. \\
BlueFin~\cite{bluefin2026} & Finance-domain agent/LLM benchmark & Spreadsheet tasks rather than executable financial ML notebooks and holdouts. \\
\bottomrule
\end{tabular}
}
\caption{Related benchmark positioning. FinDS-AgentBench targets the missing intersection of end-to-end financial ML research artifacts, temporal information discipline, leakage resistance, reproducibility, and writeup validity.}
\label{tab:related-work-positioning}
\end{table}
